---
title: "Alcohol vs Seat choice"
author: "Andrea Calderon"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??


# Introduction 

Data are from the UCDavis.csv 
Is the amount of alcohol consumed per week different for the different seating rows.

$H_0$ : There is no difference in the average amount of alcohol consumed per week based in seating row


$H_A$ : There is a difference in the average amount of alcohol consumed per week based in seating row

# Methods 

alcohol is numeric variable. 

Seat is a categorical variable.   


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
This boxplot shows numerical data of alcohol consumed for front , middle and back. 


## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```


Numerical summary shows that median for back seats consumptions is 3.5, front seat cosumption is 0.0, and middle seat is 1.0.


## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
## Conclusions


