---
title: "Alcohol vs Seat choice"
author: "Andrea Calderon"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??


# Introduction 

Data are from the UCDavis.csv 
Is the amount of alcohol consumed per week different for the different seating rows.

$H_0$ : There is no difference in the average amount of alcohol consumed per week based in seating row


$H_A$ : There is a difference in the average amount of alcohol consumed per week based in seating row

# Methods 

We predict alcohol consumption based on row 
alcohol ~ Seat


alcohol is numeric variable 
Seat is a categorical variable 

so we used the numerical~cat helper file 



## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


